Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-13 Paper/gammaRays.tex
Correction to PSFs and Location Filtering

Now we have a decent set of photons, which we can use for analysis. However, some of the photons in this set are still originated from background, and not from the source. We cannot filter out these photons, but we can substitute a linear component of background by estimating it from a long time period before the burst. In order to perform this computation, we'll need an exposure map, which will be discussed in the following section.

>>>>

Now we have a decent set of photons, which we can use for analysis. However, some of the photons in this set are still originated from background, and not from the source. We cannot filter out these photons, but we can substitute a linear component of background estimating it from a long time period before the burst. In order to perform this computation, we need an exposure map, which will be discussed in the following section.
